### 2021-11-20 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@c8ba22b8d2ce32a5b66db878c1d33e5f28831815 🚀

\hypertarget{ch3-optimizing-corridor-placement}{%
\section{CH3 optimizing corridor
placement}\label{ch3-optimizing-corridor-placement}}

@@

>>>>

\hypertarget{chapter-three-optimizing-corridor-placement-against-ecological-dynamics}{%
\section{Chapter Three: Optimizing corridor placement against ecological
dynamics}\label{chapter-three-optimizing-corridor-placement-against-ecological-dynamics}}

As human activity

@@

\begin{figure}
\centering
\includegraphics{./figures/software.png}
\caption{todo}
\end{figure}
